Appendix

### 2019-09-24 manuscript/appendix/appendix.Rmd
with faceting

```{r}
alpha <- 0.1
training_data <- train %>% select(t,x) %>% mutate(reps="1", set = "training", alpha = 1)

true_forecast <- 
  future_map_dfr(1:100, 
                 function(reps) sim(may, p), 
                 .id = "reps"
                 ) %>% 
  mutate(t = t+2000,
         set = "true",
         alpha = alpha) %>% 
  bind_rows(training_data)

predicted_forecast <- posterior_sims %>% 
    mutate(t = t+2000,
           set = "predicted",
           alpha = alpha)
```

```{r}
bind_rows(predicted_forecast, true_forecast) %>% 
  ggplot(aes(t,x)) +
  geom_line(aes(group = interaction(reps, set), col = set), alpha = .05) + 
  geom_line(data = training_data) + 
  scale_color_solarized()
```

>>>>

```{r}
alpha <- 0.1
training_data <- train %>% select(t,x) %>% mutate(reps="1") #, set = "training")

true_forecast <- 
  future_map_dfr(1:100, 
                 function(reps) sim(may, p), 
                 .id = "reps"
                 ) %>% 
  mutate(t = t+2000) %>% 
  bind_rows(training_data) %>% 
  mutate(set = "true")

predicted_forecast <- 
  posterior_sims %>% 
    mutate(t = t+2000) %>%
    bind_rows(training_data) %>% 
    mutate(set = "predicted")
```

```{r}
bind_rows(predicted_forecast, true_forecast) %>% 
#predicted_forecast %>%
  ggplot(aes(t,x)) +
  geom_line(aes(group = interaction(reps, set), col = set), alpha = .05) + 
  geom_line(data = training_data) + 
  facet_wrap(~set) + 
  scale_color_solarized()
```
